%-------------------------------------------------------------------------------
%	SECTION TITLE
%-------------------------------------------------------------------------------
\cvsection{Research Experience}
%-------------------------------------------------------------------------------
%	CONTENT
%-------------------------------------------------------------------------------
\newcommand{\ecoli}{\emph{E. coli }}
\newcommand{\ejub}{\emph{E. jubatus }}
\newcommand{\gal}{\emph{G. g. domesticus}}
\begin{cventries}
%---------------------------------------------------------
  \cventry
    {Research Assistant} % Job title
    {University of Michigan - Glotzer Group} % Organization
    {} % Location
    {Oct 2015 - Present} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed a mean-field simulation technique for the molecular dynamics of anisotropic particles and optimized it for modern GPUs.
        \item Employed a novel coarse-graining approach to explain the assembly of supercharged protein oligomers.
        \item Built ML models and deep neural networks using scikit-learn and TensorFlow to identify drivers of protein crystallization.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Thesis Researcher} % Job title
    {Princeton University - Prud'homme Lab} % Organization
    {} % Location
    {Sep 2012 - Jun 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Characterized phase separation in specific polymer blends to ameliorate effects of depletion flocculation.
	    \item Developed nanoparticles and gel microparticles for incorporation into a targeted drug delivery system for lung cancer.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Academy of Sciences of the Czech Republic - Ettrich Lab} % Organization
    {} % Location
    {Jul 2012 - Jun 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Used all-atom molecular dynamics simulations to discover the physical origin of the functional transition in the EcoR124i transcription factor.
      \end{cvitems}
    }
\ifoutdated
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Princeton University - Brynildsen Lab} % Organization
    {} % Location
    {Sep 2012 - Jun 2013} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Identified key reactions in the \ecoli metabolome associated with cell death from antibiotics.
        \item Helped build a model to determine whether antibiotics kill primarily by binding to specific targets or by the generation of deleterious reactive oxygen species.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Princeton University- Stone Lab} % Organization
    {} % Location
    {Feb 2012 - Jun 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Developed microfluidic chips to apply stresses to biological membranes.
        \item Studied how physical stresses relate to surface area regulation in bilipid membranes.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Princeton University - Lewis-Sigler Institute} % Organization
    {} % Location
    {Sep 2011 - Jan 2012} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Characterized an untested system for control of gene expression under Professor Botstein.
        \item Compared the effectiveness of three different systems for controlling gene expression.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Princeton University - Shvartsman Lab} % Organization
    {} % Location
    {Sep 2010 - Jan 2011} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Built a simulation of bistable reaction networks using MATLAB.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {Stanford University - Heller Lab} % Organization
    {} % Location
    {Jul 2010 - Sep 2010} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Identified the transcription factors key to cochlear stem cell development in \gal.
        \item Quantified nonzero protein expression in the developing otocyst.
      \end{cvitems}
    }
%---------------------------------------------------------
  \cventry
    {Undergraduate Researcher} % Job title
    {UC Santa Cruz - COSMOS} % Organization
    {} % Location
    {Jul 2006 - Sep 2006} % Date(s)
    {
      \begin{cvitems} % Description(s) of tasks/responsibilities
        \item Proposed a project investigating the differential survival rates of different regional stocks of the Stellar Sea Lion (\ejub).
        \item Developed complete methodology and analyzed data for potential preliminary results.
      \end{cvitems}
    }
\fi
\end{cventries}
